Local to Global Mariculture Modelling

### 2025-07-28 index.qmd
Clean up structure

## Main analysis

The main analysis for this project focuses on the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.

@@

## Extra analysis

The extra analyses for this project involved some exploration into potential impacts of nutrient losses. This will likely not make it into the final manuscript.

@@

# Model functioning

@@

fnms <- output_growth_data_path %>% 
  list.files(full.names = T) %>% 
  str_subset("reference")

df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
  as.data.frame() %>% 
  mutate(mean = set_units(mean, "g") %>% set_units("t"),
         sd = set_units(sd, "g") %>% set_units("t")) %>% 
  select(-farm_ID)

@@

df_2 <- df %>% 
  filter(t %in% min_t:max_t) %>% 
  mutate(sd = sd/mean) %>% 
  group_by(t) %>% 
  reframe(sd = sqrt(sum(sd^2)),
          mean = sum(mean),
          sd = sd*mean) %>% 
  mutate(cohort = "all",
         split = "Totalled")

@@

# Modelled experimental feeds {#sec-feeds}

@@

# Inputs {#inputs}

```{r}
#| label: farm-geometry

farm_geometry <- find_read(output_farm_data_path, "farm_geometry")
```

@@

# Code and packages used

>>>>

## Main scripts

The main scripts for this project focus on setting up the model to examine the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.

@@

## Extra scripts

The extra scripts for this project involved some exploration into potential impacts of nutrient losses. These will likely not make it into the final manuscript.

@@

# Supplemental methods {#sec-supp-methods}

@@

df <- find_read(output_model_farm_path, "dw_") %>% 
  mutate(
    mean = set_units(mean, "g") %>% set_units("t"),
    sd = set_units(sd, "g") %>% set_units("t")
  ) %>% 
  select(-farm_ID)

@@

df_2 <- df %>% 
  filter(t %in% min_t:max_t) %>% 
  group_by(t) %>% 
  reframe(
    sd_mean = sqrt(sum(sd_mean^2)),
    mean = sum(mean),
    sd = sd_mean*mean
  ) %>% 
  mutate(
    cohort = "all",
    split = "Totalled"
  )

@@

## Modelled experimental feeds {#sec-feeds}

@@

# Results {#sec-results}

@@

# Code and packages used {#sec-code}
